Poker Chips, Earthquakes, and Computation

### 2014-10-13 finaldraft.tex
typos

Let $A(0)$ be the set of nodes that are targeted by earthquakes when $i = 0$ and $A(1)$ be the set of nodes that are targeted by earthquakes when $i=1$.  We claim that $A(0) \subset A(1)$. This is true as when we set the input square to 1 we only increase the locations that can chips redistributed from them by earthquakes. However the output square is not in $A(1)$ by definition of our function, which produces a contradiction.  Therefore our current model of computation cannot have a board that computes NOT. 
\end{proof}

>>>>

Let $A(0)$ be the set of nodes that are targeted by earthquakes when $i = 0$ and $A(1)$ be the set of nodes that are targeted by earthquakes when $i=1$.  We claim that $A(0) \subset A(1)$. This is true as when we set the input square to 1 we only increase the locations that can have chips redistributed from them by earthquakes. However the output square is not in $A(1)$ by the definition of our function, which produces a contradiction. Therefore our current model of computation cannot have a board that computes NOT. 
\end{proof}
